Quantum Interval-Valued Probability: Contextuality and the Born Rule

### 2017-08-20 prop_letter.tex
prop_letter.tex \section{Introduction} Add a comment...

A principal result is that recasting the Kochen-Specker theorem in
terms of ``$\delta$-determinism'', with $\delta$ 
quantifying the effect of finite-precision uncertainties on measurement 
outcomes, reducing to the purely deterministic
Kochen-Specker case for $\delta=0$, can resolve the question of effect
of finite precision and imperfections on contextuality.  A remarkable
consequence of our analysis is that not only does the
quantum-mechanical requirement for contextuality continue to hold,
thus maintaining the Kochen-Specker result for a \emph{non-vanishing}
range of $\delta$, but that at a \emph{certain fixed value} of
$\delta$, there is a sharp transition, parallel in its consequences
to, say, a phase transition, to \emph{non-contextuality}; that is,
quantum mechanics suddenly fails to hold, and all variables can be
specified simultaneously, turning the theory effectively into a
classical theory that can be specified consistently by hidden
variables.  These results provide a new insight into the
Meyer-Mermin debate by presenting a theory in which there is a
\emph{parameter} interpolating between what appeared previously to be
irreconcilable interpretations of contextuality.

>>>>

A principal result is that recasting the Kochen-Specker theorem in
terms of ``$\delta$-determinism'', with $\delta$ 
quantifying the effect of finite-precision uncertainties on measurement 
outcomes, reducing to the purely deterministic
Kochen-Specker case for $\delta=0$, can resolve the question of effect
of finite precision and imperfections on contextuality.  A remarkable
consequence of our analysis is that not only does the
quantum-mechanical requirement for contextuality continue to hold,
thus maintaining the Kochen-Specker result for a \emph{non-vanishing}
range of $\delta$, but that at a \emph{certain fixed value} of
$\delta$, there is a sharp transition, parallel in its consequences
to, say, a phase transition, to \emph{non-contextuality}; that is,
quantum mechanics suddenly fails to hold, and all variables can be
specified simultaneously, turning the theory effectively into a
classical theory that can be specified consistently by hidden
variables.  
\yutsung{The part after ``that is'' looks strange.
\begin{enumerate}
\item The Kochen-Specker theorem is not about quantum mechanics, is about whether
quantum mechanics can be simulated by a non-contextual deterministic hidden
variable theory or not. Hence, ``quantum mechanics suddenly fails to hold''
doesn't make a lot sense.
\item The question is whether there exist a QIVPM means ``a classical theory
consistently by hidden variables.'' At least, a QIVPM is not deterministic, and
I need to check whether it qualities as a classical probabilitic hidden variable
theory\ldots(?)
\end{enumerate}
}
These results provide a new insight into the
Meyer-Mermin debate by presenting a theory in which there is a
\emph{parameter} interpolating between what appeared previously to be
irreconcilable interpretations of contextuality.
